The Precambrian paleogeography of Laurentia

### 2020-09-17 Manuscript/Laurentia_Paleogeo_Manuscript.tex
add velocity panel figure caption info and additional glossary terms

%\usepackage{lipsum}		%  Filler text
\usepackage{lettrine}
\usepackage{pdflscape}
\usepackage{longtable}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../Figures/Laurentia_paleolatitude.pdf}
\caption{\textbf{Laurentia paleolatitude through time in data and models.} Top panel: Paleolatitude implied by paleomagnetic poles from Laurentia and associated blocks for Duluth (lat=46.79\textdegree N, lon=92.10\textdegree W). The paleomagnetic poles are compiled in Table 2. Bottom panel: Paleolatitude implied by Laurentia poles compared with that implied by published paleogeographic models and the simple Laurentia model used in this chapter for the reconstructions in Figure \ref{fig:Laurentia_reconstructions}.}
\label{fig:Laurentia_paleolatitude}
\end{figure*}

@@

@@

@@

@@

@@

>>>>

%\usepackage{lipsum}		%  Filler text
\usepackage{lettrine}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{threeparttablex}

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{../Figures/Laurentia_paleolatitude.pdf}
\caption{\textbf{Laurentia paleolatitude through time in data and models.} Top panel: Paleolatitude implied by paleomagnetic poles from Laurentia and associated blocks for Duluth (lat=46.79\textdegree N, lon=92.10\textdegree W). The paleomagnetic poles are compiled in Table 2. Middle panel: Paleolatitude implied by Laurentia poles compared with that implied by published paleogeographic models and the simple Laurentia model used in this chapter for the reconstructions in Figure \ref{fig:Laurentia_reconstructions}. TC2017 refers to \cite{Torsvik2017a} and S-H 2017 refers to \cite{Swanson-Hysell2017a}. Bottom panel: velocity implied by the paleogeographic models in cm per year for the Duluth reference point on Laurentia.}
\label{fig:Laurentia_paleolatitude}
\end{figure*}

@@

\noindent\textbf{geodynamo } The mechanism whereby convective flow in Earth's fluid outer core generates Earth's magnetic field

@@

\noindent\textbf{plate tectonics } A process where the lithosphere is in distinct pieces that move relative to one another.

@@

\noindent\textbf{supercontinent } A term referring to Earth's continental lithosphere being concentrated into a large landmass. The supercontinent Pangea that existed ca. 200 Ma is the archtypal supercontinent. A threshold of 75$\%$ of extant continental crust has been proposed for a continent to be considered a supercontinent \citep{Meert2012a}.  Gondwana (Australia + India + Africa + South America) constituted $\sim$60$\%$ and was a constituent of Pangea such that \cite{Evans2016a} proposed that it and similar landmasses should be called \textbf{semi-supercontinents}.

@@

\noindent\textbf{stagnant lid } A planetary state where there is a single lithospheric plate (`lid'). The lithosphere is relatively stable and immobile in comparison to a planet with active plate tectonics where there is motion between multiple lithospheric plates.

@@

\noindent\textbf{true polar wander } The rotation of the solid Earth about the liquid outer core to maintain rotational equilibrium. This process results in Earth's lithosphere undergoing a single coherent rotation relative to the spin axis.
